Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-01-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: adjusted order of sections

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-2}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
% \usepackage{txfonts}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

@@

@@

Also,
%
\begin{equation}
\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
= \left[
\frac{\ell c^2 (1 + z)}{G M}
\right]^{p}
\end{equation}
%

\subsection{Overview of modified gravity theories}
\label{sec:review_theories}

@@

\subsubsection{scalar-Gauss-Bonnet gravity}
%
This theory is given by the following action,
%
\begin{equation} \label{eq:action_sgb}
    S_{\rm GB} = \frac{1}{16 \pi}
    \int \dV
    \left[
    R - \tfrac{1}{2}(\nabla \varphi)^2
    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \mathscr{G}
    \right],
\end{equation}
%
where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
invariant $\mathscr{G}$,
%
\begin{equation} \label{eq:def_gb}
    \mathscr{G} =
    R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
    - 4 R^{\mu\nu}R_{\mu\nu}
    + R^2,
\end{equation}
%
with strength set by the dimensionful coupling constant $\agb$ with dimensions
of length.

@@

\subsubsection{dynamical Chern-Simons}

@@

\subsubsection{Effective-field-theory of GR}

@@

>>>>

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
% \usepackage{txfonts}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

@@

% -----------
% Bibligraphy
% -----------
\AtBeginDocument{%
    \newwrite\bibnotes
    \def\bibnotesext{Notes.bib}
    \immediate\openout\bibnotes=\jobname\bibnotesext
    \immediate\write\bibnotes{@CONTROL{REVTEX41Control}}
    \immediate\write\bibnotes{@CONTROL{%
    apsrev41Control,author="08",editor="1",pages="1",title="0",year="1"}}
    \if@filesw
    \immediate\write\@auxout{\string\citation{apsrev41Control}}%
    \fi
}

@@

\section{Overview of modified gravity theories}
\label{sec:review_theories}

@@

\subsection{scalar-Gauss-Bonnet gravity}
%
This theory is given by the following action,
%
\begin{equation} \label{eq:action_sgb}
    S_{\rm GB} = \frac{1}{16 \pi}
    \int \dV
    \left[
    R - \tfrac{1}{2}(\nabla \varphi)^2
    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \mathscr{G}
    \right],
\end{equation}
%
where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
invariant $\mathscr{G}$,
%
\begin{equation} \label{eq:def_gb}
    \mathscr{G} =
    R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
    - 4 R^{\mu\nu}R_{\mu\nu}
    + R^2,
\end{equation}
%
with strength set by the dimensionful coupling constant $\agb$ with dimensions
of length.

@@

\subsection{dynamical Chern-Simons}

@@

\subsection{Effective-field-theory of GR}

@@

Also,
%
\begin{equation}
\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
= \left[
\frac{\ell c^2 (1 + z)}{G M}
\right]^{p}
\end{equation}
